Placeholder

### 2021-02-18 Paper_Histograms.Rmd
Adjusted the heights of the non-white retro graph in the age, gender, employ and ethnicity retro plot

grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, 
          nrow = 2,
          bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,
                            hjust = 1,
                            gp = gpar(fontface = 3L, fontsize = 9)))

>>>>

grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, 
          nrow = 2,
          heights=c(1, 1.2),
          bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,
                            hjust = 1,
                            gp = gpar(fontface = 3L, fontsize = 9)))
